### 2016-07-27 notions.tex
privacy
cheers

\section{Security Notions}
\label{sec:security-notions}
\tsnote{intro text}
As highlighted by Naor and Yogev, Equation~(\ref{eqn:correctness}) is a non-adaptive version of correctness;
we are interested in defining an adaptive (i.e., adversarial) notion
of correctness.   Figure~\ref{fig:correctness} describes a security experiment 
that captures such a notion.

@@

First, a set~$S$ is chosen according to some
distribution~$\distr{\calS}{}$ over the collection of multisets
$\mathcal{S}$ associated to~$\Pi=(\Rep,\Qry)$, and then
$\Rep(S)$ is run to generate $(M,\aux)$.
%(Unless stated otherwise, we assume security holds for all distributions and thus for all sets $S$.)
Adversary~$A$ is given~$\calS$ and $\aux$~as input; it is
provided an oracle~$\TestOracle$ that, on input a query~$q \in \calQ$,
computes (and returns) the result of $\Qry(M,\aux,q)$, and increments
a counter if this result is in error.  The adversary wins if it
manages to cause at least~$r>0$ such errors among its queries.

@@

\def\bin{{\sf Bin}}
\heading{Observations on trivial attacks. } 
Let~$\Pi$ be a scheme that is $\epsilon$-correct, and consider an attack that 
asks random queries $q_1,q_2,\ldots,q_T$, i.e., uniform samples from~$\calQ$.
%The expected number of random queries needed to
%find a error is $1/\epsilon$ tries; thus, an attacker making $O(t/\epsilon)$ queries succeeds with constant probability (almost always).
%Actually, it seems worthwhile to formalize this. 
Let $X_i$ be a random variable indicating the event $\Qry(M,\aux,q_i)\neq q_i(S)$.  
The $\epsilon$-correctness of~$\Pi$ guarantees that the probability that $X_i=1$ is at most~$\epsilon$, 
and it is tempting to model the~$X_i$ as i.i.d. Bernoulli trials with success probability~$\epsilon$.
However, a moment's reflection shows that this is not the case.  Concretely, consider the following scheme.  Fix $|S|=n$ for all $S \in \calS$, where $n \ll |\univ|$.  For the queries, let $\calQ = \{q_x\colon \calS \to \bits \,|\, \forall x \in \univ\}$ where $\forall S \in \calS$ the predicate $q_x(S)=1 \Leftrightarrow x \in S$.  Let $\Rep(S)$ pick a random element~$s \in S$, and return $M = S \setminus \{s\}$ and $\aux = \emptystring$.  To respond to queries, let~$\Qry(M,\aux,q_x)=1$ iff $x \in M$.  It is easy to see that this scheme is $1/n$-correct; for any fixed~$S$, there are exactly~$n$ queries~$q_x$ that have probability~$1/n$  (over the coins of~$\Rep$) of causing a correctness error, and the remaining $|\univ|-n$ queries have probability zero of causing an error.  Moreover, once the coins of~$\Rep$ are fixed, there is exactly \emph{one} query that will cause an error.  Thus for random queries from~$Q$, for all~$i\in[T]$ we have $\Prob{X_i=1}=1/|\univ| \ll 1/n = \epsilon$.

This example is contrived, but the point is that $\epsilon$-correctness is measured over the coins of~$\Rep$, for a fixed~$S$ and query~$q$; once the coins of~$\Rep$ are fixed, it is not straightforward how to connect~$\epsilon$ to events that depend on other sources of randomness. \tsnote{Not sure if there's more to say in this section, or if what's here is already too much.}

@@

\subsection{Notions of Privacy}
One can also consider the orthogonal notion of privacy for a set-representation.
\jnote{Actually, I am now unsure what the right way to define it is. It seems natural
to give the attacker $\aux$. But if we give them $\aux$ and $M$ then they have everything.
If $S$ has high min-entropy (element-wise), then it might still be
possible to have security here.}\tsnote{I think we will always bump up
against the (element-wise) min-entropy of the distribution over~$S$,
at least in the ``one-wayness'' style definition that I had been imagining. }
There are several possible definitions:
\begin{enumerate}
\item A ``one-wayness'' definition where $S$ has high min-entropy (element-wise), and we
give the attacker $\aux$ and either $M$ or oracle access to $\Qry$. The attacker
succeeds if it can output an element in~$S$.

@@

\begin{figure}[htp]
\centering
\hfpages{.45}{
\hpagess{.5}{.45}
{
\experimentv{$\ExpWPriv{\setprim,\distr{\calS}{}}{A}$}\\
$S \getsr \distr{\calS}{}$\\
$(M,\aux) \getsr \Rep(S)$\\
$z \getsr A^{\TestOracle}(\aux)$\\
if $z \in S$ then Return 1\\
Return 0

\medskip
\experimentv{$\ExpPriv{\setprim,\distr{\calS}{}}{A}$}\\
$S \getsr \distr{\calS}{}$\\
$(M,\aux) \getsr \Rep(S)$\\
$z \getsr A(M,\aux)$\\
if $z \in S$ then Return 1\\
Return 0\\
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\aux,q)$\\
Return~$a$
}
}
%
{
\hpagess{.5}{.475}
{
\experimentv{$\ExpPrivInd{\setprim,\distr{\calS}{}}{A}$}\\
$b \getsr \bits$\\
$z \getsr A^{\RepOracle,\TestOracle}$\\
if $z = b$ then Return 1\\
Return 0\\
}
%
{
%\oracle{$\RepOracle(S_0,S_1)$}\\
\oracle{$\RepOracle()$}\\
if $\mathrm{used}=\true$ then Ret $\bot$\\
%if $|S_0|\neq|S_1|$ then \\
%\nudge Ret $\bot$\\
$S_0,S_1 \getsr \distr{\calS}{}$\\
$\mathrm{used}=\true$\\
$(M,\aux) \getsr \Rep(S_b)$\\
Return $(S_0,S_1,\aux)$\\

\medskip
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\aux,q)$\\
Return~$a$\\
}
}
\caption{Privacy notions. {\bf Left:} ``One-wayness'' style
  definitions. The top is a weaker notion, because the representation
  is hidden from the adversary. {\bf Right:} An
  ``indistinguishability'' style notion. (Still playing...)} 
\label{fig:privacy}
\end{figure}

>>>>

\section{Security Notions}
\label{sec:security-notions}
\tsnote{intro text}
Following NY, we are interested in defining an adaptive (i.e.,
adversarial) notion of correctness.   Figure~\ref{fig:correctness} describes a security experiment 
that captures such a notion.

@@

First, a set~$S$ is chosen according to some
distribution~$\distr{\calS}{}$ over the collection of multisets
$\mathcal{S}$ associated to~$\Pi$, and then
$\Rep(S)$ is run to generate $(M,\aux)$.
%(Unless stated otherwise, we assume security holds for all distributions and thus for all sets $S$.)
Adversary~$A$ is given~$\calS$ and $\aux$~as input; it is
provided an oracle~$\TestOracle$ that, on input a query~$q \in \calQ$,
computes (and returns) the result of $\Qry(M,\aux,q)$, and increments
a counter if this result is in error.  The adversary wins if it
manages to cause at least~$r>0$ such errors among its queries.

@@

\def\bin{{\sf Bin}}
\heading{Observations on trivial attacks. } 
Let~$\Pi$ be a scheme that is $(1-\epsilon)$-correct, and consider an attack that 
asks random queries $q_1,q_2,\ldots,q_T$, i.e., uniform samples from~$\calQ$.
%The expected number of random queries needed to
%find a error is $1/\epsilon$ tries; thus, an attacker making $O(t/\epsilon)$ queries succeeds with constant probability (almost always).
%Actually, it seems worthwhile to formalize this. 
Let $\mathrm{Err}_i$ be a random variable indicating the event $\Qry(M,\aux,q_i)\neq q_i(S)$.  
The $(1-\epsilon)$-correctness of~$\Pi$ guarantees that the probability that $\mathrm{Err}_i=1$ is at most~$\epsilon$, 
and it is tempting to model the~$\mathrm{Err}_i$ as i.i.d. Bernoulli trials with success probability~$\epsilon$.
However, a moment's reflection shows that this is not the case.  Concretely, consider the following scheme.  Fix $|S|=n$ for all $S \in \calS$, where $n \ll |\univ|$.  For the queries, let $\calQ = \{q_x\colon \calS \to \bits \,|\, \forall x \in \univ\}$ where $\forall S \in \calS$ the predicate $q_x(S)=1 \Leftrightarrow x \in S$.  Let $\Rep(S)$ pick a random element~$s \in S$, and return $M = S \setminus \{s\}$ and $\aux = \emptystring$.  To respond to queries, let~$\Qry(M,\aux,q_x)=1$ iff $x \in M$.  It is easy to see that this scheme is $1/n$-correct; for any fixed~$S$, there are exactly~$n$ queries~$q_x$ that have probability~$1/n$  (over the coins of~$\Rep$) of causing a correctness error, and the remaining $|\univ|-n$ queries have probability zero of causing an error.  Moreover, once the coins of~$\Rep$ are fixed, there is exactly \emph{one} query that will cause an error.  Thus for random queries from~$Q$, for all~$i\in[T]$ we have $\Prob{\mathrm{Err}_i=1}=1/|\univ| \ll 1/n = \epsilon$.

This example is contrived, but it highlights the important difference
between error-probability and error-rate.  In particular, the
error-probability~$\epsilon$ is measured only over the coins
of~$\Rep$, for a fixed~$S$ and query~$q$.
Once the coins of~$\Rep$ are fixed, it is not straightforward how to
connect~$\epsilon$ to events that depend on other sources of
randomness. \tsnote{Not sure if there's more to say in this section, or if what's here is already too much.}

@@

\subsection{Notions of Privacy}
One can also consider the orthogonal notion of privacy for a set-representation.
\jnote{Actually, I am now unsure what the right way to define it is. It seems natural
to give the attacker $\aux$. But if we give them $\aux$ and $M$ then they have everything.
If $S$ has high min-entropy (element-wise), then it might still be
possible to have security here.}\tsnote{I think we will always bump up
against the (element-wise) min-entropy of the distribution over~$S$,
at least in the ``one-wayness'' style definition that I had been imagining. }
There are several possible definitions:
\begin{enumerate}
\item A ``one-wayness'' definition where $S$ has high min-entropy (element-wise), and we
give the attacker $\aux$ and either $M$ or oracle access to $\Qry$. The attacker
succeeds if it can output an element in~$S$. \tsnote{Neither of these seems to capture the Neidermeier et al. attack.  Giving the adversary~$M$ is closest, but our syntax would put the hash function secret keys into~$M$, which the Neidermeier attack doesn't get.}

@@

\begin{figure}[htbp]
\centering
\hfpages{.495}{
\hpagess{.5}{.45}
{
\experimentv{$\ExpWPriv{\setprim,\distr{\calS}{}}{A}$}\\
$S \getsr \distr{\calS}{}$\\
$(M,\aux) \getsr \Rep(S)$\\
$z \getsr A^{\TestOracle}(\aux)$\\
if $z \in S$ then Return 1\\
Return 0\\

\medskip
\experimentv{$\ExpPriv{\setprim,\distr{\calS}{}}{A}$}\\
$S \getsr \distr{\calS}{}$\\
$(M,\aux) \getsr \Rep(S)$\\
$z \getsr A(M,\aux)$\\
if $z \in S$ then Return 1\\
Return 0\\
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\aux,q)$\\
Return~$a$
}
}
%
{
\hpagess{.485}{.5}
{
\experimentv{$\ExpPrivInd{\setprim,\distr{\calS}{}}{A}$}\\
$b \getsr \bits$\\
$S_0,S_1 \getsr \distr{\calS}{}$\\
$(M,\aux) \getsr \Rep(S_b)$\\
$b' \getsr A^{\TestOracle}(S_0,S_1,\aux)$\\
if $b' = b$ then Return 1\\
Return 0\\
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\aux,q)$\\
Return~$a$\\

\medskip
\oracle{$\RepOracle(S_0,S_1)$}\\
if $\mathrm{used}=\true$ then Return $\bot$\\
%if $|S_0|\neq|S_1|$ then \\
%\nudge Ret $\bot$\\
$S_0,S_1 \getsr \distr{\calS}{}$\\
$\mathrm{used}=\true$\\
$(M,\aux) \getsr \Rep(S_b)$\\
Return $(S_0,S_1,\aux)$\\

}
}
\caption{Privacy notions. {\bf Left:} ``One-wayness'' style
  definitions. The top is a weaker notion, because the representation
  is hidden from the adversary. {\bf Right:} An
  ``indistinguishability'' style notion. (Still playing... ignore unused oracles)} 
\label{fig:privacy}
\end{figure}
